Objective-first optimization for nanophotonics

### 2011-07-29 presentations/group-pres_2011-08-04.tex
Started on structure constraint section.

\oursection{Structure constraint: level-set method}
\BIT
\item a more detailed statement of our problem is
\begin{align}
\mbox{decrease} & \quad \|g(x,p)\|^2 \\
\subjectto & \quad f(x) = 0 \\
        & \quad p \in \{p_\text{can be made}\}
\end{align}
\item need to constrain possible $p$ to what can be fabricated
\item for nanophotonics this means two distinct materials only
\item using $p \in \{\epsilon_1, \epsilon_2\}$ defeats the purpose of using linear approximations
\item need to \emph{incrementally} update the topology of the structure
\EIT

>>>>

\oursection{Structure constraint: level-set method}
\BIT
\item a more detailed statement of our problem is
\begin{align}
\mbox{decrease} & \quad \|g(x,p)\|^2 \\
\subjectto & \quad f(x) = 0 \\
        & \quad p \in \{p_\text{manufacturable}\}
\end{align}
\item need to constrain possible $p$ to what can be fabricated
\item for nanophotonics this means two distinct materials only
\item however, using $p \in \{\epsilon_1, \epsilon_2\}$ defeats the purpose of using linear approximations
\EIT
\newpage

\BIT
\item need ability to \emph{incrementally} update the topology of the structure
\item describe $p$ using the \emph{interface} between the two materials
\item implicitly describe boundary using the \emph{level-set} of a higher-dimensional function
\begin{center}
\includegraphics[width=0.45\textwidth]{../figures/level-set.jpg} \\
source: \url{http://en.wikipedia.org/wiki/Level_set_method}
\end{center}
\EIT
\newpage

\BIT
\item ...
\begin{center}
\includegraphics[width=0.8\textwidth]{../figures/structure-progression.jpg} \\
\end{center}
\EIT
